Towards Patient-Specific Neural Field Modeling using Micro-Electrode Data

### 2011-05-13 ltx/data_paper/DataPaper.tex
edit to plot captions

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelBasis1.pdf}
\end{center}
\caption{{\bf Connectivity kernel support estimate.} The estimated support of the kernel is shown by the red circle. Black area shows the non-zero values of the support after thresholding. A $5\times5$ grid of basis functions (blue circles) used to reconstruct the connectivity kernel.}
\label{fig:KernelWidthEstimation}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/DisturbanceWidthEstimation.pdf}
\end{center}
\caption{{\bf Disturbance support estimation}.}
\label{fig:DisturbanceWidthEstimation}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelEstimate.pdf}
\end{center}
\caption{{\bf Connectivity kernel estimates over 100 realisations.} left: True kernel; right;Estimated kernel.}
\label{fig:KernelEstimates}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelEstimateCrossSection.pdf}
\end{center}
\caption{{\bf Cross-section of connectivity kernel estimates over 100 realisation.} True is blue; Estimate is green; 95\% Confedence interval is red.}
\label{fig:KernelEstimateCrossSection}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/Histogram.pdf}
\end{center}
\caption{{\bf Synaptic dynamic parameter and hyperparameter estimates}.}
\label{fig:Histogram}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics[scale=1]{./Figures/FieldEstimates.pdf}
\end{center}
\caption{{\bf Field Estimates}. }
\label{fig:FieldEstimates}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/Q.pdf}
\end{center}
\caption{{\bf Lower-bound of the log-likelihood}. $Q(\boldsymbol\Theta',\boldsymbol\Theta')=-(T-1)\left[n_y(1+\ln \hat{\sigma}^2_{\epsilon})+ n_x(1+\ln \hat{\sigma}^2_d)\right]$.}
\label{fig:LowerBound}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

>>>>

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelBasis1.pdf}
\end{center}
\caption{{\bf Connectivity kernel support approximation.} The approximate support of the kernel is shown by the red circle. Black area shows the non-zero values of the support after thresholding. A $5\times5$ grid of basis functions (blue circles) used to reconstruct the connectivity kernel.}
\label{fig:KernelWidthEstimation}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/DisturbanceWidthEstimation.pdf}
\end{center}
\caption{{\bf Disturbance support approximation}. }
\label{fig:DisturbanceWidthEstimation}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelEstimate.pdf}
\end{center}
\caption{{\bf Connectivity kernel estimates.} (A) Actual kernel. (B) The mean kernel estimate over 100 realisations}
\label{fig:KernelEstimates}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelEstimateCrossSection.pdf}
\end{center}
\caption{{\bf Cross-sections of connectivity kernel estimates.} Actual kernel and the mean kernel estimates are shown with blue and green lines respectively. Each of the estimate from Monte Carlo simulation is shown with black line. The 95\% confidence intervals are shown by shaded red area.}
\label{fig:KernelEstimateCrossSection}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/Histogram.pdf}
\end{center}
\caption{{\bf Synaptic dynamic parameter and hyperparameter estimates}.}
\label{fig:Histogram}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics[scale=1]{./Figures/FieldEstimates.pdf}
\end{center}
\caption{{\bf Field Estimates}. }
\label{fig:FieldEstimates}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/Q.pdf}
\end{center}
\caption{{\bf Lower-bound of the log-likelihood}. $Q(\boldsymbol\Theta',\boldsymbol\Theta')=-(T-1)\left[n_y(1+\ln \hat{\sigma}^2_{\epsilon})+ n_x(1+\ln \hat{\sigma}^2_d)\right]$.}
\label{fig:LowerBound}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
